How do changes in ex vary between countries?

### 2022-03-03 draft_paper.Rmd
typo corrected

-[ ] Introduction to be written once methods/results discussed and decided on

@@

- England & Wales (`GBRTENW`)
- Scotland (`GBR_SCO`)
- UK as a whole (`GBR_UK`) #we gaven't included UK but can do
- France (`FRANTP`)
- Spain (`ESP`)
- Italy (`ITA`)
- Germany
   - Total Germany (`DEUTNP`)
   - East Germany (`DEUTE`)
   - West Germany (`DEUTW`)
   - Simulated/Synthetic Germany

@@

####Are the differences by decade statistically significant? 
To assess whether the changes by decade are statistically significant, we carried out [Jon please could you write a little more here?]
We found the only significant change decade-on-decades was for East Germany for females at birth and at aged 65 years...

>>>>

- [ ] Introduction to be written once methods/results discussed and decided on

@@

- England & Wales (`GBRTENW`)
- Scotland (`GBR_SCO`)
- UK as a whole (`GBR_UK`) #we haven't included UK but can do
- France (`FRANTP`)
- Spain (`ESP`)
- Italy (`ITA`)
- Germany
   - Total Germany (`DEUTNP`)
   - East Germany (`DEUTE`)
   - West Germany (`DEUTW`)
   - Simulated/Synthetic Germany

@@

###Are the differences by decade statistically significant? 
To assess whether the changes by decade are statistically significant, we carried out [Jon please could you write a little more here?]
We found the only significant change decade-on-decades was for East Germany for females at birth and at aged 65 years...
